timesliced_random_cell_selection

### 2018-11-09 src/raster_sjl.Rmd
full loop check - thunderbirds are go!

>>>>

checkt the temp

```{r}
test1.1 <- extract(x=row1rast[[1]], y = testrow1sp)
test1.1
test2.1 <- extract(x=row1rast[[1]], y = testrow2sp)
test2.1
test3.1 <- extract(x=row3rast[[1]], y = testrow3sp)
test3.1
test4.1 <- extract(x=row3rast[[1]], y = testrow4sp)
test4.1
test5.1 <- extract(x=row3rast[[1]], y = testrow5sp)
test5.1
test6.1 <- extract(x=row2rast[[1]], y = testrow6sp)
test6.1
test7.1 <- extract(x=row2rast[[1]], y = testrow7sp)
test7.1
```
yes!!
